### 2018-08-01 paper/design.tex
minor and my plan, now attacking my parts on the design

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

A device's availability depends on its user's behaviour, hence the device must 
predict this behaviour.
This is best done jointly between the user's all devices.
In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

@@

\include*{sphinxes}
\include*{spor}
\include*{squad-overlay-design}
\include*{file-transfer-design}

>>>>

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

A device's availability depends on its user's behavior, hence the device must 
predict this behavior.
This is best done jointly between the user's all devices.
In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
compute their own availability prediction function based on the observations by 
all other devices.

@@

\include*{sphinxes}
\include*{spor}
\commentAL{What I want to do from here:
(1) The squad overlay, where a user's devices exchange behavioral information;
(2) Predicting a device's availability;
(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
(4) File exchange.}
\include*{squad-overlay-design}
\include*{file-transfer-design}
